---
title: "02 curbage_recognition Analyses: Edited"
output: html_notebook
---
### Angelique I. Delarazan
#### 04/19/2022

1. Performs two-way ANOVAs on target recognition and lure (2 x 2 ANOVA: Domain Type [Narrarive v. Perceptual] x Age [Older v. Younger]). Dependent variables: dprime (z[Target Hit Rate] – z[Foil False Alarm Rate]) and LDI (p[New|Lure] - p[Old|Foil])

2. Performs mixed models on the previous data on Target Recognition (d') and LDI with recall of verifiable details as a random effect.

3. Calculates raw response proportions across age groups (Older vs. Younger) and domain (Narrative vs. Perceptual). 

4. Calculates mean and standard deviation of neuropsychological test scores for older adults.

Note: Data cleaning required (see jupyter notebook: 01_curbage_recognition_data_cleaning.ipynb)

### Set Up
```{r}
#Import Libraries
library(tidyverse)
library(dplyr)
library(rstatix)
library(emmeans)
library(afex)
```

```{r}
recognition = read_csv("/Volumes/GAMMA/curbage_recognition/reviews/analyses/data/sub-all_group-all_task-recognition_desc-all_results_neuropsych.csv")
recognition$subject = as.numeric(recognition$subject)
recognition$group = as.factor(recognition$group)
recognition$type = as.factor(recognition$type)
recognition$LDI = as.numeric(recognition$LDI_reviewer)
recognition$group_type = as.factor(recognition$group_type)
recognition$dprime = as.numeric(recognition$dprime)
```
```{r}
recall = read_csv("/Volumes/GAMMA/curbage_behavioral/experiment1/data/recall/sub-all_task-recall_desc-scored.csv")

recall$subject = as.numeric(recall$SUBID)
recall$scene = as.factor(recall$Scene)
recall$narrative01 = as.numeric(recall$NarrativeVerifiableDetails_JD)
recall$narrative02 = as.numeric(recall$NarrativeVerifibleDetails_EM)
recall$perceptual01 = as.numeric(recall$PerceptualVerifiableDetails_JD)
recall$perceptual02 = as.numeric(recall$PerceptualVerifiableDetails_EM)

recall = subset(recall, select = c("subject", "scene", "narrative01", "narrative02", "perceptual01", "perceptual02"))
```

```{r}
recall = recall %>% 
  mutate(group = if_else(
    subject < 300, "older",
    if_else(
      subject > 300, "younger",
      "blah"
    )
  ))
```
```{r}
recall = recall[(recall$subject != 999),] %>% 
  group_by(subject, group, scene) %>% 
  summarise(recall_narrative = ((narrative01 + narrative02)/2),
            recall_perceptual = ((perceptual01 + perceptual02)/2)) %>% 
  group_by(subject, group) %>% 
  summarise(total_narrative = sum(recall_narrative), total_perceptual = sum(recall_perceptual))
```
```{r}
all = merge(recall, recognition, by = c("subject", "group"))
```

### 2 x 2 Mixed ANOVA: (Within: Narrative vs. Perceptual) and (Between: Older vs. Younger)

#### Figure 2a. Perform two-way ANOVA on Target Recognition (d')
Target recognition was assessed in terms of normalized d' values (z[Target Hit Rate] – z[Foil False Alarm Rate]) derived from signal detection analysis.

2 x 2 ANOVA: Domain Type (Perceptual v. Narrative) x Age (Younger v. Older Adults)
```{r}
#excluded participant: recognition[(recognition$subject!=307),]
stats_aov = aov_ez(id="subject",dv="dprime",data=recognition,between="group",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~group*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```

#### Figure 2b. Perform two-way ANOVA on Lure Discrimination (LDI)
Response bias was corrected by calculating a lure discrimination index (LDI) for each subject (p(New|Lure) - p(Old|Foil))

2 x 2 ANOVA: Domain Type (Perceptual v. Narrative) x Age (Younger v. Older Adults)
```{r}
stats_aov = aov_ez(id="subject",dv="LDI",data=recognition,between="group",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~group*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```

#### Run mixed models on the previous data on Target Recognition (d') with verifiable details as a random effect.
Target recognition was assessed in terms of normalized d' values (z[Target Hit Rate] – z[Foil False Alarm Rate]) derived from signal detection analysis.
```{r}
stats_test = lmer(dprime ~ type * group + (1|total_narrative), data = all)
summary(stats_test)

coef(summary(stats_test))

#emmeans(stats_test, pairwise ~ group * type, adjust = "bonferroni")
```
#### Run mixed models on the previous data on LDI with MoCA_total as a random effect.
Response bias was corrected by calculating a lure discrimination index (LDI) for each subject (p(New|Lure) - p(Old|Foil))
```{r}
stats_test = lmer(LDI ~ type * group + (1|recall_narrative), data = all)
summary(stats_test)

coef(summary(stats_test))

emmeans(stats_test, pairwise ~ group * type, adjust = "bonferroni")
```

### Table 2. Raw response proportions across age groups (Older vs. Younger) and domain (Narrative vs. Perceptual). 
Note: Change domain_type and/or age_group below.
```{r}
domain_type = "narrative"
age_group = "older"

# mean(SD) Target Hit Rate
mean(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$target_hit_rate, na.rm=TRUE)
sd(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$target_hit_rate, na.rm=TRUE)

# mean(SD) Lure Correct Rejection Rate
mean(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$lure_cr_rate, na.rm=TRUE)
sd(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$lure_cr_rate, na.rm=TRUE)

# mean(SD) Foil Correct Rejection Rate
mean(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
sd(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
```


### Table 1. Neuropsychological test scores form older adults (N = 21). Scores are presented as mean (SD).
```{r}
recognition %>% 
  group_by(group) %>% 
  summarise(MoCA_mean = mean(MoCA_total), 
            MoCA_sd = sd(MoCA_total), 
            Craft21_immediate_mean = mean(Craft21_immediate_total),
            Craft21_immediate_sd = sd(Craft21_immediate_total),
            Craft21_delayed_mean = mean(Craft21_delayed_total),
            Craft21_delayed_sd = sd(Craft21_delayed_total),
            MINT_mean = mean(MINT_total),
            MINT_sd = sd(MINT_total)
            )
```

