---
title: "02 curbage_recognition Analyses"
output: html_notebook
---
### Angelique I. Delarazan
#### 04/19/2022

1. Performs two-way ANOVAs on target recognition and lure (2 x 2 ANOVA: Domain Type [Narrarive v. Perceptual] x Age [Older v. Younger])

2. Calculates correlations between neuropsychological tests and target recognition & lure performance

3. Split on MoCA: Incorporate a test of cognitive abilities in Analysis #1 above

Note: Data cleaning required (see jupyter notebook: 01_curbage_recognition_data_cleaning.ipynb)

### Set Up
```{r}
#Import Libraries
library(tidyverse)
library(dplyr)
library(rstatix)
library(emmeans)
library(afex)
```

```{r}
recognition = read_csv("/Volumes/GAMMA/curbage_recognition/data/sub-all_group-all_task-recognition_desc-all_results_neuropsych.csv")
recognition$subject = as.numeric(recognition$subject)
recognition$group = as.factor(recognition$group)
recognition$type = as.factor(recognition$type)
recognition$LDI = as.numeric(recognition$LDI)
recognition$group_type = as.factor(recognition$group_type)
recognition$dprime = as.numeric(recognition$dprime)
```

### Analyses
#### Figure 2a. Perform two-way ANOVA on Target Recognition (d')
Target recognition was assessed in terms of normalized d' values (z[Target Hit Rate] – z[Foil False Alarm Rate]) derived from signal detection analysis.

2 x 2 ANOVA: Domain Type (Perceptual v. Narrative) x Age (Younger v. Older Adults)
```{r}
#excluded participant: recognition[(recognition$subject!=307),]
stats_aov = aov_ez(id="subject",dv="dprime",data=recognition,between="group",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~group*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```

#### Figure 2b. Perform two-way ANOVA on Lure Discrimination (LDI)
Response bias was corrected by calculating a lure discrimination index (LDI) for each subject (p[New|Lure] – p[New|Target])

2 x 2 ANOVA: Domain Type (Perceptual v. Narrative) x Age (Younger v. Older Adults)
```{r}
stats_aov = aov_ez(id="subject",dv="LDI",data=recognition,between="group",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~group*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```

#### Table 1. Raw response proportion responses.
Note: Change domain_type and/or age_group below.
```{r}
domain_type = "narrative"
age_group = "older"

# mean(SD) Target Hit Rate
mean(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$target_hit_rate, na.rm=TRUE)
sd(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$target_hit_rate, na.rm=TRUE)

# mean(SD) Lure Correct Rejection Rate
mean(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$lure_cr_rate, na.rm=TRUE)
sd(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$lure_cr_rate, na.rm=TRUE)

# mean(SD) Foil Correct Rejection Rate
mean(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
sd(recognition[(recognition$group==age_group)&(recognition$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
```

### Table 2. Correlations with Neuropsycholgical Tests. 
Note: Change neuropsych (e.g., MoCA_total, Craft21_immediate_total, 
Craft21_delayed_total, MINT_total) and/or domain_type (e.g., "narrative" or "perceptual").
```{r}
neuropsych = recognition$MoCA_total
domain_type = "narrative"

# mean(SD) of neuropsych score
mean(neuropsych, na.rm = TRUE)
sd(neuropsych, na.rm = TRUE)

# correlations (pearson's) between neuropsych and dprime or LDI subset by domain type.
cor.test(formula = ~ recognition$dprime + neuropsych, subset = recognition$type == domain_type)
cor.test(formula = ~ recognition$LDI + neuropsych, subset = recognition$type == domain_type)
```

### Split on MOCA
MoCA scores range from 0-30, and a score of 26 or higher is generally considered as “normal.” Given that our older adult sample exhibited heterogeneity in falling above or below a MoCA score of 26, we incorporated a simple contrast of cognitive ability in our analyses via split based on MoCA score. Older participants were categorized in two groups: Lower MoCA Scores (MoCA score < 26) and Higher MoCA Scores (MoCA score >= 26).

#### Subset dataframe to low and high MoCA scorers
```{r}
younger = filter(recognition, group=="younger")
older_low_MoCA = filter(recognition, MoCA_total<26)
older_high_MoCA = filter(recognition, MoCA_total>25)
low_MoCA = rbind(younger, older_low_MoCA)
high_MoCA = rbind(younger, older_high_MoCA)
```

#### Table 2. Raw correct response proportions (Low & High MoCA Scorers).
Low MoCA Scorers
```{r}
domain_type = "narrative"
age_group = "older"

# mean(SD) Target Hit Rate
mean(older_low_MoCA[(older_low_MoCA$type==domain_type),]$target_hit_rate, na.rm=TRUE)
sd(older_low_MoCA[(older_low_MoCA$type==domain_type),]$target_hit_rate, na.rm=TRUE)

# mean(SD) Lure Correct Rejection
mean(older_low_MoCA[(older_low_MoCA$type==domain_type),]$lure_cr_rate, na.rm=TRUE)
sd(older_low_MoCA[(older_low_MoCA$type==domain_type),]$lure_cr_rate, na.rm=TRUE)

# mean(SD) Foil Correct Rejection
mean(older_low_MoCA[(older_low_MoCA$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
sd(older_low_MoCA[(older_low_MoCA$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
```

High MoCA Scorers
```{r}
domain_type = "narrative"
age_group = "older"

# mean(SD) Target Hit Rate
mean(older_high_MoCA[(older_high_MoCA$type==domain_type),]$target_hit_rate, na.rm=TRUE)
sd(older_high_MoCA[(older_high_MoCA$type==domain_type),]$target_hit_rate, na.rm=TRUE)

# mean(SD) Lure Correct Rejection
mean(older_high_MoCA[(older_high_MoCA$type==domain_type),]$lure_cr_rate, na.rm=TRUE)
sd(older_high_MoCA[(older_high_MoCA$type==domain_type),]$lure_cr_rate, na.rm=TRUE)

# mean(SD) Foil Correct Rejection
mean(older_high_MoCA[(older_high_MoCA$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
sd(older_high_MoCA[(older_high_MoCA$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
```

### Low MoCA Scorers
#### Perform two-way ANOVA on Target Recognition (d') on Low MoCA scorers
Target recognition was assessed in terms of normalized d' values (z[Target Hit Rate] – z[Foil False Alarm Rate]) derived from signal detection analysis.

Figure 3a. 2 x 2 ANOVA: Domain Type (Perceptual v. Narrative) x Age (Younger v. Older Adults)
```{r}
stats_aov = aov_ez(id="subject",dv="dprime",data=low_MoCA,between="group",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~group*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```

#### Perform two-way ANOVA on Lure Discrimination (LDI) on Low MoCA scorers
Response bias was corrected by calculating a lure discrimination index (LDI) for each subject (p[New|Lure] – p[New|Target])

Figure 3c. 2 x 2 ANOVA: Domain Type (Perceptual v. Narrative) x Age (Younger v. Older Adults)
```{r}
stats_aov = aov_ez(id="subject",dv="LDI",data=low_MoCA,between="group",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~group*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```

### High MoCA Scorers
#### Perform two-way ANOVA on Target Recognition (d') on High MoCA scorers
Target recognition was assessed in terms of normalized d' values (z[Target Hit Rate] – z[Foil False Alarm Rate]) derived from signal detection analysis.

Figure 3b. 2 x 2 ANOVA: Domain Type (Perceptual v. Narrative) x Age (Younger v. Older Adults)
```{r}
stats_aov = aov_ez(id="subject",dv="dprime",data=high_MoCA,between="group",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~group*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```

#### Perform two-way ANOVA on Lure Discrimination (LDI) on High MoCA scorers
Response bias was corrected by calculating a lure discrimination index (LDI) for each subject (p[New|Lure] – p[New|Target])

Figure 3d. 2 x 2 ANOVA: Domain Type (Perceptual v. Narrative) x Age (Younger v. Older Adults)
```{r}
stats_aov = aov_ez(id="subject",dv="LDI",data=high_MoCA,between="group",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~group*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```

#### Run 03_curbage_recognition_figures.Rmd to generate figures.











































