---
title: "03 curbage_recognition Figures"
output: html_notebook
---

### Angelique I. Delarazan
#### 04/19/2022
Generates figures for the curbage paper:

1. Swamplots of two-way ANOVAs on target recognition and lure (2 x 2 ANOVA: Domain Type [Narrarive v. Perceptual] x Age [Older v. Younger])

2. Swamplots of two-way ANOVAs on target recognition and lure (2 x 2 ANOVA: Domain Type [Narrarive v. Perceptual] x Age [Older v. Younger]) after split on MoCA among older adult sample

3. Legend

Export figures as 800 x 800 or larger.

Note: Data cleaning completed using Python (see jupyter notebook: 01_curbage_recognition_data_cleaning.ipynb) and analyses conducted using R (see 02_curbage_recognition_analyses.Rmd)

### Set Up
```{r}
#Import Libraries
library(tidyverse)
library(ggplot2)
library(ggsignif)
library(ggpubr)
library(dplyr)
library(ggbeeswarm)
```

```{r}
recognition = read_csv("/Volumes/GAMMA/curbage_recognition/data/sub-all_group-all_task-recognition_desc-all_results_neuropsych.csv")
recognition$subject = as.numeric(recognition$subject)
recognition$group = as.factor(recognition$group)
recognition$type = as.factor(recognition$type)
recognition$LDI = as.numeric(recognition$LDI)
recognition$group_type = as.factor(recognition$group_type)
recognition$dprime = as.numeric(recognition$dprime)
```

### Figure 2a. Swarmplot of dprime for all subjects.
```{r fig.width = 6}
#dprime

#dprime_all = 
  recognition %>% 
  ggplot(aes(x = type, group = group, y = dprime, col = group)) +
  ylab("Target Recognition (d')
       ") + xlab("Test Domain") + labs(title = "") + 
  coord_cartesian(ylim = c(0.8, 5.5)) +
  geom_beeswarm(dodge.width = 1, size = 5, alpha = 0.7) +
  stat_summary(fun = mean, na.rm = TRUE, 
               geom = "point",
               size = 3, color = "black", 
               position = position_dodge(width = 1)) +
  stat_summary(fun.data = mean_cl_normal, na.rm = TRUE, 
               geom = "errorbar", width = 0.2, color = "black",
               position = position_dodge(width = 1),
               size = 1) +
  scale_color_manual("group",values = c("older"="#da7b5e","younger"="#5d747c"), labels = c("older"="Older","younger"="Younger")) +
  theme(legend.position = "none", 
        plot.title = element_text(size = 48),   
        axis.text.y = element_text(size = 32), 
        axis.text.x = element_text(size = 32),
        axis.title = element_text(size = 32),
        legend.text=element_text(size=24),
        legend.title = element_blank())+ 
  scale_x_discrete(labels=c("narrative"="Narrative", "perceptual"="Perceptual"))  +
  geom_signif(y_position = c(4.5,5.1), 
            xmin = c(0.8,1.3), xmax = c(1.7,2.2),
            size = 1,
            annotation = c("*","**"), tip_length = 0, textsize = 12, color = "black") +
  scale_y_continuous(breaks=c(1.0,2.0,3.0,4.0,5.0), labels = scales::number_format(accuracy = 0.1))
```

### Figure 2b. Swarmplot of LDI for all subjects.
```{r fig.width = 6}
#LDI

#LDI_all = 
  recognition %>% 
  group_by(subject) %>% 
  ggplot(aes(x = type, group = group, y = LDI, col = group)) +
  ylab("Lure Discrimination (LDI)
       ") + xlab("Test Domain") + labs(title = "") + 
  coord_cartesian(ylim = c(0, 1.2)) +
  geom_beeswarm(dodge.width = 1, size = 5, alpha = 0.7) +
  stat_summary(fun = mean, na.rm = TRUE, 
               geom = "point",
               size = 3, color = "black", 
               position = position_dodge(width = 1)) +
  stat_summary(fun.data = mean_se, na.rm = TRUE, 
               geom = "errorbar", width = 0.2, color = "black",
               position = position_dodge(width = 1),
               size = 1) +
  scale_color_manual("group",values = c("older"="#da7b5e","younger"="#5d747c"), labels = c("older"="Older","younger"="Younger")) +
  geom_signif(y_position = c(1.1, 1), 
            xmin = c(0.8,1.8), xmax = c(1.7,2.2),
            size = 1,
            annotation = c("+","**"), tip_length = 0, textsize = 12, color = "black") +
  theme(legend.position = "none", 
        plot.title = element_text(size = 48),   
        axis.text.y = element_text(size = 32), 
        axis.text.x = element_text(size = 32),
        axis.title = element_text(size = 32),
        legend.text=element_text(size=24),
        legend.title = element_blank())+ 
  scale_x_discrete(labels=c("narrative"="Narrative", "perceptual"="Perceptual"))  +
  scale_y_continuous(breaks=c(0.0,0.5,1.0))
```


### Split on MOCA
MoCA scores range from 0-30, and a score of 26 or higher is generally considered as “normal.” Given that our older adult sample exhibited heterogeneity in falling above or below a MoCA score of 26, we incorporated a simple contrast of cognitive ability in our analyses via split based on MoCA score. Older participants were categorized in two groups: Lower MoCA Scores (MoCA score < 26) and Higher MoCA Scores (MoCA score >= 26).

#### Subset dataframe to low and high MoCA scorers
```{r}
younger = filter(recognition, group=="younger")
older_low_MoCA = filter(recognition, MoCA_total<26)
older_high_MoCA = filter(recognition, MoCA_total>25)
low_MoCA = rbind(younger, older_low_MoCA)
high_MoCA = rbind(younger, older_high_MoCA)
```

### Figure 3a. Swarmplot of d' for low MoCA scorers.
```{r fig.width = 6}

dprime_low = 
  low_MoCA %>% 
  ggplot(aes(x = type, group = group, y = dprime, col = group)) +
  ylab("Target Recognition (d')
       ") + xlab("Test Domain") + labs(title = "", subtitle = expression("Younger vs. Older"[italic("(Low MoCA Scorer)")])) + 
  coord_cartesian(ylim = c(0.8, 5.5)) +
  geom_beeswarm(dodge.width = 1, size = 5, alpha = 0.7) +
  stat_summary(fun = mean, na.rm = TRUE, 
               geom = "point",
               size = 3, color = "black", 
               position = position_dodge(width = 1)) +
  stat_summary(fun.data = mean_se, na.rm = TRUE, 
               geom = "errorbar", width = 0.2, color = "black",
               position = position_dodge(width = 1),
               size = 1) +
  scale_color_manual("group",values = c("older"="#da7b5e","younger"="#5d747c"), labels = c("older"="Older","younger"="Younger")) +
  geom_signif(y_position = c(5.1), 
            xmin = c(1.3), xmax = c(2.2),
            size = 1,
            annotation = c("***"), tip_length = 0, textsize = 12, color = "black") +
  theme(legend.position = "none", 
        plot.title = element_text(size = 48),   
        axis.text.y = element_text(size = 32), 
        axis.text.x = element_text(size = 32),
        axis.title = element_text(size = 32),
        legend.text=element_text(size=24),
        legend.title = element_blank(), 
        plot.subtitle = element_text(hjust=0.5, size = 30, color = 'grey28'),
        )+
  scale_x_discrete(labels=c("narrative"="Narrative", "perceptual"="Perceptual"))  +
  scale_y_continuous(breaks=c(1.0,2.0,3.0,4.0,5.0), labels = scales::number_format(accuracy = 0.1))

dprime_low
```
### Figure 3b. Swarmplot of d' for high MoCA scorers.
```{r fig.width = 6}

dprime_high = 
  high_MoCA%>% 
  ggplot(aes(x = type, group = group, y = dprime, col = group))  +
  ylab("Target Recognition (d')
       ") + xlab("Test Domain") + labs(title = "", subtitle = expression("Younger vs. Older"[italic("(High MoCA Scorer)")])) + 
  coord_cartesian(ylim = c(0.8, 5.5)) +
  geom_beeswarm(dodge.width = 1, size = 5, alpha = 0.7) +
  stat_summary(fun = mean, na.rm = TRUE, 
               geom = "point",
               size = 3, color = "black", 
               position = position_dodge(width = 1)) +
  stat_summary(fun.data = mean_se, na.rm = TRUE, 
               geom = "errorbar", width = 0.2, color = "black",
               position = position_dodge(width = 1),
               size = 1) +
  scale_color_manual("group",values = c("older"="#da7b5e","younger"="#5d747c"), labels = c("older"="Older","younger"="Younger")) +
  geom_signif(y_position = c(4.5,5.1), 
            xmin = c(0.8,1.3), xmax = c(1.7,2.2),
            size = 1,
            annotation = c("***","***"), tip_length = 0, textsize = 12, color = "black") +
  theme(legend.position = "none", 
        plot.title = element_text(size = 48),   
        axis.text.y = element_text(size = 32), 
        axis.text.x = element_text(size = 32),
        axis.title = element_text(size = 32),
        legend.text=element_text(size=24),
        legend.title = element_blank(), 
        plot.subtitle = element_text(hjust=0.5, size = 30, color = 'grey28'),
        )+
  scale_x_discrete(labels=c("narrative"="Narrative", "perceptual"="Perceptual"))  +
  scale_y_continuous(breaks=c(1.0,2.0,3.0,4.0, 5.0), labels = scales::number_format(accuracy = 0.1))

dprime_high
```

### Figure 3c. Swarmplot of LDI for low MoCA scorers.
```{r fig.width = 6}

LDI_low = 
  low_MoCA %>% 
  ggplot(aes(x = type, group = group, y = LDI, col = group))  +
  ylab("Lure Discrimination (LDI)
       ") + xlab("Test Domain") + labs(title = "", subtitle = expression("Younger vs. Older"[italic("(Low MoCA Scorer)")])) + 
  coord_cartesian(ylim = c(0, 1.2)) +
  geom_beeswarm(dodge.width = 1, size = 5, alpha = 0.7) +
  stat_summary(fun = mean, na.rm = TRUE, 
               geom = "point",
               size = 3, color = "black", 
               position = position_dodge(width = 1)) +
  stat_summary(fun.data = mean_se, na.rm = TRUE, 
               geom = "errorbar", width = 0.2, color = "black",
               position = position_dodge(width = 1),
               size = 1) +
  scale_color_manual("group",values = c("older"="#da7b5e","younger"="#5d747c"), labels = c("older"="Older","younger"="Younger")) +
  geom_signif(y_position = c(1.1, 1), 
            xmin = c(0.8,1.8), xmax = c(1.7,2.2),
            size = 1,
            annotation = c("*","**"), tip_length = 0, textsize = 12, color = "black") +
  theme(legend.position = "none", 
        plot.title = element_text(size = 48),   
        axis.text.y = element_text(size = 32), 
        axis.text.x = element_text(size = 32),
        axis.title = element_text(size = 32),
        legend.text=element_text(size=24),
        legend.title = element_blank(), 
        plot.subtitle = element_text(hjust=0.5, size = 28, color = 'grey28'),
        )+
  scale_x_discrete(labels=c("narrative"="Narrative", "perceptual"="Perceptual"))  +
  scale_y_continuous(breaks=c(0.0,0.5,1.0))

LDI_low
```

### Figure 3d. Swarmplot of LDI for low MoCA scorers.
```{r fig.width = 6}

LDI_high = 
  high_MoCA %>% 
  ggplot(aes(x = type, group = group, y = LDI, col = group))   +
  ylab("Lure Discrimination (LDI)
       ") + xlab("Test Domain") + labs(title = "", subtitle = expression("Younger vs. Older"[italic("(High MoCA Scorer)")])) + 
  coord_cartesian(ylim = c(0, 1.2)) +
  geom_beeswarm(dodge.width = 1, size = 5, alpha = 0.7) +
  stat_summary(fun = mean, na.rm = TRUE, 
               geom = "point",
               size = 3, color = "black", 
               position = position_dodge(width = 1)) +
  stat_summary(fun.data = mean_se, na.rm = TRUE, 
               geom = "errorbar", width = 0.2, color = "black",
               position = position_dodge(width = 1),
               size = 1) +
  scale_color_manual("group",values = c("older"="#da7b5e","younger"="#5d747c"), labels = c("older"="Older","younger"="Younger")) +
  theme(legend.position = "none", 
        plot.title = element_text(size = 48),   
        axis.text.y = element_text(size = 32), 
        axis.text.x = element_text(size = 32),
        axis.title = element_text(size = 32),
        legend.text=element_text(size=24),
        legend.title = element_blank(), 
        plot.subtitle = element_text(hjust=0.5, size = 28, color = 'grey28'),
        )+
  scale_x_discrete(labels=c("narrative"="Narrative", "perceptual"="Perceptual")) +
  scale_y_continuous(breaks=c(0.0,0.5,1.0))

LDI_high
```

### Generate Legend.
Note: Change + theme(legend.position = " ",... to "right" or "top" to make the legend long or wide format, respectively.
```{r fig.width = 2}
legend = recognition %>% 
  ggplot(aes(x = type, group = group, y = LDI, col = group)) +
  ylab("") + xlab("") + labs(title = "", subtitle = "Younger vs. High MoCA Score Older") + 
  coord_cartesian(ylim = c(0, 1.10)) +
  geom_beeswarm(dodge.width = 1, size = 5, alpha = 0.8) +
  stat_summary(fun = mean, na.rm = TRUE, 
               geom = "point",
               size = 3, color = "black", 
               position = position_dodge(width = 1)) +
  stat_summary(fun.data = mean_se, na.rm = TRUE, 
               geom = "errorbar", width = 0.2, color = "black",
               position = position_dodge(width = 1),
               size = 1) +
  scale_color_manual("group",values = c("older"="#da7b5e","younger"="#5d747c"), labels = c("older"="Older   ","younger"="Younger")) +
  theme(legend.position = "top", 
        plot.title = element_text(size = 48),   
        axis.text.y = element_text(size = 32), 
        axis.text.x = element_text(size = 32),
        axis.title = element_text(size = 32),
        legend.text=element_text(size=24),
        legend.title = element_blank(),
        plot.subtitle = element_text(hjust=0.5, size = 28, color = 'grey28')
        )+
  scale_x_discrete(labels=c("narrative"="Narrative", "perceptual"="Perceptual")) 
  scale_x_discrete(labels=c("narrative"="Narrative", "perceptual"="Perceptual"))

as_ggplot(get_legend(legend))
```












































