---
title: "04 curbage_recognition Analyses: Supplemental Materials"
output: html_notebook
---

### Angelique I. Delarazan
#### 04/19/2022

### Set Up
```{r}
#Import Libraries
library(tidyverse)
library(dplyr)
library(rstatix)
library(emmeans)
library(afex)
```

```{r}
recognition = read_csv("/Volumes/GAMMA/curbage_recognition/reviews/analyses/data/sub-all_group-all_task-recognition_desc-all_results_neuropsych.csv")
recognition$subject = as.numeric(recognition$subject)
recognition$group = as.factor(recognition$group)
recognition$type = as.factor(recognition$type)
recognition$LDI = as.numeric(recognition$LDI_reviewer)
recognition$group_type = as.factor(recognition$group_type)
recognition$dprime = as.numeric(recognition$dprime)
```
```{r}
recall = read_csv("/Volumes/GAMMA/curbage_behavioral/experiment1/data/recall/sub-all_task-recall_desc-scored.csv")

recall$subject = as.numeric(recall$SUBID)
recall$scene = as.factor(recall$Scene)
recall$narrative01 = as.numeric(recall$NarrativeVerifiableDetails_JD)
recall$narrative02 = as.numeric(recall$NarrativeVerifibleDetails_EM)
recall$perceptual01 = as.numeric(recall$PerceptualVerifiableDetails_JD)
recall$perceptual02 = as.numeric(recall$PerceptualVerifiableDetails_EM)

recall = subset(recall, select = c("subject", "scene", "narrative01", "narrative02", "perceptual01", "perceptual02"))
```

```{r}
recall = recall %>% 
  mutate(group = if_else(
    subject < 300, "older",
    if_else(
      subject > 300, "younger",
      "blah"
    )
  ))
```
```{r}
recall = recall[(recall$subject != 999),] %>% 
  group_by(subject, group, scene) %>% 
  summarise(recall_narrative = ((narrative01 + narrative02)/2),
            recall_perceptual = ((perceptual01 + perceptual02)/2)) %>% 
  group_by(subject, group) %>% 
  summarise(total_narrative = sum(recall_narrative), total_perceptual = sum(recall_perceptual))
```
```{r}
all = merge(recall, recognition, by = c("subject", "group"))
```

### Recall
Supplementary Table 2. Total Verifiable Details in Recall
```{r}
recall %>% 
  group_by(group) %>% 
  summarise(mean_narrative = mean(total_narrative),
            sd_narrative = sd(total_narrative),
            mean_perceptual = mean(total_perceptual),
            sd_perceptual = sd(total_perceptual))
```

```{r}
t.test(recall$total_narrative ~ recall$group, paired = FALSE, var.equal = FALSE)
```


### Supplemental Table 3. Neuropsychological test scores for older adults, and correlations between these scores and recognition performance on Narrative and Perceptual test domain.
```{r}
cor.test(all[(all$group_type=="older_narrative"),]$MoCA_total, all[(all$group_type=="older_narrative"),]$dprime)
cor.test(all[(all$group_type=="older_perceptual"),]$Craft21_immediate_total, all[(all$group_type=="older_perceptual"),]$dprime)
cor.test(all[(all$group_type=="older_narrative"),]$Craft21_delayed_total, all[(all$group_type=="older_narrative"),]$dprime)
cor.test(all[(all$group_type=="older_perceptual"),]$MINT_total, all[(all$group_type=="older_perceptual"),]$dprime)
```
```{r}
cor.test(all[(all$group_type=="older_narrative"),]$MoCA_total, all[(all$group_type=="older_narrative"),]$LDI)
cor.test(all[(all$group_type=="older_perceptual"),]$Craft21_immediate_total, all[(all$group_type=="older_perceptual"),]$LDI)
cor.test(all[(all$group_type=="older_narrative"),]$Craft21_delayed_total, all[(all$group_type=="older_narrative"),]$LDI)
cor.test(all[(all$group_type=="older_perceptual"),]$MINT_total, all[(all$group_type=="older_perceptual"),]$LDI)
```

### Split on MoCA
#### Subset dataframe to low and high MoCA scorers
```{r}
younger = filter(all, group=="younger")
older_low_MoCA = filter(all, MoCA_total<26)
older_high_MoCA = filter(all, MoCA_total>25)
low_MoCA = rbind(younger, older_low_MoCA)
high_MoCA = rbind(younger, older_high_MoCA)
```

#### Table 2. Raw correct response proportions (Low & High MoCA Scorers).
Low MoCA Scorers
```{r}
domain_type = "narrative"

# mean(SD) Target Hit Rate
mean(older_low_MoCA[(older_low_MoCA$type==domain_type),]$target_hit_rate, na.rm=TRUE)
sd(older_low_MoCA[(older_low_MoCA$type==domain_type),]$target_hit_rate, na.rm=TRUE)

# mean(SD) Lure Correct Rejection
mean(older_low_MoCA[(older_low_MoCA$type==domain_type),]$lure_cr_rate, na.rm=TRUE)
sd(older_low_MoCA[(older_low_MoCA$type==domain_type),]$lure_cr_rate, na.rm=TRUE)

# mean(SD) Foil Correct Rejection
mean(older_low_MoCA[(older_low_MoCA$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
sd(older_low_MoCA[(older_low_MoCA$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
```

High MoCA Scorers
```{r}
domain_type = "narrative"

# mean(SD) Target Hit Rate
mean(older_high_MoCA[(older_high_MoCA$type==domain_type),]$target_hit_rate, na.rm=TRUE)
sd(older_high_MoCA[(older_high_MoCA$type==domain_type),]$target_hit_rate, na.rm=TRUE)

# mean(SD) Lure Correct Rejection
mean(older_high_MoCA[(older_high_MoCA$type==domain_type),]$lure_cr_rate, na.rm=TRUE)
sd(older_high_MoCA[(older_high_MoCA$type==domain_type),]$lure_cr_rate, na.rm=TRUE)

# mean(SD) Foil Correct Rejection
mean(older_high_MoCA[(older_high_MoCA$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
sd(older_high_MoCA[(older_high_MoCA$type==domain_type),]$foil_cr_rate, na.rm=TRUE)
```
### Categorize as low, high MoCA older and younger
```{r}
all_older = all[(all$subject<300),] %>% 
  mutate(MoCA_condition = if_else(MoCA_total<26, "1_low_MoCA",
         if_else(MoCA_total>25, "2_high_MoCA",
         "wtf")))
```

```{r}
all_younger = filter(all, group=="younger")
all_younger$MoCA_condition = "3_younger"
```

```{r}
recognition_MoCA = rbind(all_older, all_younger)
```

Uncomment for Supplemental Figure 2.
```{r}
#recognition_MoCA$MoCA_condition = paste0(recognition_MoCA$MoCA_condition, "_", recognition_MoCA$type)
```

#### Figure 2a. Perform two-way ANOVA on Target Recognition (d')
Target recognition was assessed in terms of normalized d' values (z[Target Hit Rate] – z[Foil False Alarm Rate]) derived from signal detection analysis.

2 x 3 ANOVA: Domain Type (Perceptual v. Narrative) x Age (Younger v. Older Adults)
```{r}
#excluded participant: recognition[(recognition$subject!=307),]
stats_aov = aov_ez(id="subject",dv="dprime",data=recognition_MoCA[(recognition_MoCA$subject!=307),],between="MoCA_condition",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~MoCA_condition*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```

```{r}
#excluded participant: recognition[(recognition$subject!=307),]
stats_aov = aov_ez(id="subject",dv="LDI",data=recognition_MoCA[(recognition_MoCA$subject!=307),],between="MoCA_condition",within="type", fun_aggregate = mean)
stats_aov
stats_posthoc = emmeans(stats_aov,~MoCA_condition*type,contr = "pairwise", adjust = "bonferroni")
stats_posthoc
```
